%%%%%%%%%%
% Lexicon
%%%%%%%%%%
\pdfbookmark[0]{Greek-English Lexicon}{lex}
\thispagestyle{plain}
\begin{center}
{\Huge GREEK-ENGLISH LEXICON}
\end{center}
\newpage

\pagestyle{fancy}
\cfoot{\gr{\thepage}}
\lhead{\large\gr{STOIQEIWN}}
\rhead{\large GREEK--ENGLISH LEXICON}

{\small
\twocolumn
\noindent ABBREVIATIONS: {\em act} - active;
{\em adj} - adjective; {\em adv} - adverb; {\em conj} - conjunction; {\em fut} - future; {\em gen} - genitive; {\em imperat} - imperative; {\em impf} - imperfect;
{\em ind} - indeclinable; {\em indic} - indicative;
{\em intr} - intransitive; {\em mid} - middle; {\em neut} - neuter;
{\em no} - noun; 
{\em par} - particle; {\em part} - participle; {\em pass} - passive; {\em perf} - perfect;
{\em pre} - preposition; {\em pres} - present; {\em pro} - pronoun; {\em sg} - singular;
{\em tr} - transitive; {\em vb} - verb.
\baselineskip 1ex

\begin{description}
\item [\gr{>'agw},] \gr{>'axw, >'hgagon, ->~hqa, >~hgmai, >'hqjhn} :  {\em vb}, lead, draw (a line).
\item[\gr{>ad'unatoc -on}]: {\em adj}, impossible.
\item[\gr{>ae'i}]: {\em adv}, always, for ever.
\item[\gr{a<ir'ew, a<ir'hsw, e[~<i]lon, <'h|rhka, <'h|rhmai, <h|r'ejhn}]:
{\em vb}, grasp.
\item[\gr{>ait'ew, a>it'hsw, >'hthsa, >'h|thka, >'h|thmai, >h|t'hjh}]: {\em vb}, postulate.
\item[\gr{a>'ithma -atoc, t'o}]: {\em no}, postulate.
\item[\gr{>ak'oloujoc -on}]: {\em adj}, analogous, consequent on, in conformity with.
\item[\gr{>'akroc -a -on}]: {\em adj}, outermost, end, extreme.
\item[\gr{>all'a}]: {\em conj}, but, otherwise.
\item[\gr{>'alogoc -on}]: {\em adj}, irrational.
\item[\gr{<'ama}]: {\em adv}, at once, at the same time, together.
\item[\gr{>amblug'wnioc -on}]: {\em adj}, obtuse-angled; \gr{t`o >amblug'wnion}, {\em no}, obtuse angle.
\item[\gr{>ambl'uc -e~ia -'u}]: {\em adj}, obtuse.
\item[\gr{>amf'oteroc -a -on}]: {\em pro}, both.
\item[\gr{>anagr'afw}]: {\em vb}, describe (a figure); see \gr{gr'afw}.
\item[\gr{>analog'ia, <h}]: {\em no}, proportion, (geometric) progression.
\item[\gr{>an'alogoc -on}]: {\em adj}, proportional.
\item[\gr{>an'apalin}]: {\em adv}, inverse(ly).
\item[\gr{anaplhr'ow}]: {\em vb}, fill up.
\item[\gr{>anastr'efw}]: {\em vb}, turn upside down, convert (ratio); see \gr{str'efw}.
\item[\gr{>anastrof'h, <h}]: {\em no}, turning upside down, conversion (of ratio).
\item[\gr{>anjufair'ew}]: {\em vb}, take away in turn; see \gr{a<ir'ew}.
\item[\gr{>an'isthmi}]: {\em vb}, set up; see \gr{>'isthmi}.
\item[\gr{>'anisoc -on}]: {\em adj}, unequal, uneven.
\item[\gr{>antip'asqw}]: {\em vb}, be reciprocally proportional; see \gr{p'asqw}.
\item [\gr{>'axwn -onoc, <o}]: {\em vb}, axis.
\item[\gr{<'apax}]: {\em adv}, once.
\item[\gr{<'apac, <'apasa, <'apan}]: {\em adj}, quite all, the whole.
\item[\gr{>'apeiroc -on}]: {\em adj}, infinite.
\item[\gr{>apenant'ion}]: {\em ind}, opposite.
\item[\gr{>ap'eqw}]: {\em vb}, be far from, be away from; see \gr{>'eqw}.
\item[\gr{>aplat'hc -'ec}]: {\em adj}, without breadth.
\item[\gr{>ap'odeixic -ewc, <h}]: {\em no}, proof.
\item[\gr{>apokaj'isthmi}]: {\em vb}, re-establish, restore; see \gr{>'isthmi}.
\item[\gr{>apolamb'anw}]: {\em vb}, take from, subtract from, cut off from; see \gr{lamb'anw}.
\item[\gr{>apot'emnw}]: {\em vb}, cut off, subtend.
\item[\gr {>ap'otmhma -atoc, t'o}]: {\em no}, piece cut off, segment.
\item[\gr{>apotom'h, <h}]: {\em vb}, piece cut off, apotome.
\item[\gr{<'aptw, <'ayw, <~hya,} ---, \gr{<~hmmai}, ---]: {\em vb},  touch, join, meet.
\item[\gr{>ap'wteroc -a -on}]: {\em adj}, further off.
\item[\gr{>'ara}]: {\em par}, thus, as it seems (inferential).
\item [\gr{>arijm'oc, <o}]: {\em no}, number.
\item[\gr{>arti'akic}]: {\em adv}, an even number of times.
\item[\gr{arti'opleuroc -on}]: {\em adj}, having a even number of sides.
\item[\gr{>'arqw, >'arxw, >~hrxa, >~hrqa, >~hrgmai, >~hrqjhn}]: {\em vb},
rule; {\em mid.}, begin.
\item[\gr{>as'ummetroc -on}]: {\em adj}, incommensurable.
\item[\gr{>as'umptwtoc -on}]: {\em adj}, not touching, not meeting.
\item[\gr{>'artioc -a -on}]: {\em adj}, even, perfect.
\item[\gr{>'atmhtoc -on}]: {\em adj}, uncut.
\item[\gr{>at'opoc -on}]: {\em adj}, absurd, paradoxical.
\item[\gr{a>ut'ojen}]: {\em adv}, immediately, obviously.
\item[\gr{>afa'irew}]: {\em vb},  take from, subtract from, cut off from;
see \gr{a<ir'ew}.
\item[\gr{<af'h, <h}]: {\em no}, point of contact.
\item[\gr{b'ajoc -eoc, t'o}]: {\em no}, depth, height.
\item[\gr{ba'inw, -b'hsomai, -'ebhn, b'ebhka,} ---, ---]: {\em vb}, walk; {\em perf}, stand (of angle).
\item[\gr{b'allw, bal~w, >'ebalon, b'eblhka, b'eblhmai, >ebl'hjhn}]:
{\em vb}, throw.
\item[\gr{b'asic -ewc, <h}]: {\em no}, base (of a triangle).
\item[\gr{g'ar}]: {\em conj}, for (explanatory).
\item[\gr{g'i[g]nomai, gen'hsomai, >egen'omhn, g'egona, geg'enhmai,} ---]:
{\em vb},\\ happen, become.
\item [\gr{gn'wmwn -onoc, <h}]: {\em no}, gnomon.
\item[\gr{gramm'h, <h}]: {\em no}, line.
\item[\gr{gr'afw, gr'ayw, >'egra[y}$\!/\!$\gr{f]a, g'egrafa, g'egrammai, >eray'amhn}]:
{\em vb}, draw (a figure).
\item[\gr{gwn'ia, <h}]: {\em no},  angle.
\item[\gr{de~i}]: {\em vb}, be necessary; \gr{de~i}, {\rm it is necessary};
\gr{>'edei}, {\rm it was necassary}; \gr{d'eon},  {\rm being necessary}.
\item[\gr{de'iknumi, de'ixw, >'edeixa, d'edeiqa, d'edeigmai, >ede'iqjhn}]: {\em vb}, show, demonstrate.
\item[\gr{deikt'eon}]: {\em ind}, one must show.
\item[\gr{de~ixic -ewc, <h}]: {\em no}, proof.
\item[\gr{dekag'wnoc -on}]: {\em adj}, ten-sided; \gr{t`o dekag'wnon},
{\em no}, decagon.
\item[\gr{d'eqomai, d'exomai, >edex'amhn,} ---, \gr{d'edegmai, >ed'eqjhn}]: {\em vb}, receive, accept.
\item[\gr{d'h}]: {\em conj}, so (explanatory).
\item[\gr{dhlad'h}]: {\em ind}, quite clear, manifest.
\item[\gr{d~hloc -h -on}]: {\em adj}, clear.
\item[\gr{dhlon'oti}]: {\em adv}, manifestly.
\item[\gr{di'agw}]: {\em vb}, carry over, draw through, draw across; see \gr{>'agw}.
\item[\gr{diag'wnioc -on}]: {\em adj}, diagonal.
\item[\gr{diale'ipw}]: {\em vb}, leave an interval between.
\item[\gr{di'ametroc -on}]: {\em adj}, diametrical; \gr{<h di'ametroc}, {\em no}, diameter, diagonal.
\item[\gr{dia'iresic -ewc, <h}]: {\em no}, division, separation.
\item[\gr{diair'ew}]: {\em vb}, divide (in two); \gr{diarej'entoc -h -on}, {\em adj}, separated (ratio); see \gr{a<ir'ew}.
\item[\gr{di'asthma -atoc, t'o}]: {\em no}, radius.
\item[\gr{diaf'erw}]: {\em vb}, differ; see \gr{f'erw}.
\item[\gr{d'idwmi, d'wsw, >'edwka, d'edwka, d'edomai, >ed'ojhn}]:
{\em vb}, give.
\item[\gr{dimo'iroc -on}]: {\em adj}, two-thirds.
\item[\gr{diplasi'azw}]: {\em vb}, double.
\item[\gr{dipl'asioc -a -on}]: {\em adj}, double, twofold.
\item[\gr{diplas'iwn -on}]: {\em adj}, double, twofold.
\item[\gr{diplo~uc -~h -o~un}]: {\em adj}, double.
\item[\gr{d'ic}]: {\em adv}, twice.
\item[\gr{d'iqa}]: {\em adv}, in two, in half.
\item[\gr{diqorom'ia, <h}]: {\em no}, point of bisection.
\item[\gr{du'ac -'adoc, <h}]: {\em no}, the number two, dyad.
\item[\gr{d'unamai}]: {\em vb}, be able, be capable, generate, square, be when squared; \gr{dunam'enh, <h}, {\em no}, 
square-root (of area)---{\em i.e.}, strai\-ght-line whose square is equal to a given area.
\item[\gr{d'unamic -ewc, <h}]: {\em no}, power (usually 2nd power when used in mathematical sence, hence), square.
\item[\gr{dunat'oc -'h -'on}]: {\em adj}, possible.
\item[\gr{dwdek'aedroc -on}]: {\em adj}, twelve-sided.
\item[\gr{<eauto~u -~hc -o~u}]: {\em adj}, of him/her/it/self, his/her/its/own.
\item[\gr{>egg'iwn -on}]: {\em adj}, nearer, nearest.
\item[\gr{>eggr'afw}]: {\em vb}, inscribe; see \gr{gr'afw}.
\item[\gr{e>~idoc -eoc, t'o}]: {\em no}, figure, form, shape.
\item[\gr{e>ikos'aedroc -on}]: {\em adj}, twenty-sided.
\item[\gr{e>'irw}/\gr{l'egw, >er~w}/\gr{er'ew,  e>~ipon, e>'irhka, e>'irhmai, >err'hjhn}]: {\em vb},\\  say, speak; {\em per pass part}, \gr{eirhm'enoc -h -on}, {\em adj}, said, aforementioned.
\item[\gr{e>'ite} \ldots \gr{e>'ite}]: {\em ind}, either \ldots or.
\item[\gr{<'ekastoc -h -on}]: {\em pro}, each, every one.
\item[\gr{<ekat'eroc -a -on}]: {\em pro}, each (of two).
\item[\gr{>ekb'allw}]: {\em vb},  produce (a line); see \gr{b'allw}. 
\item[\gr{>ekj'ew}]: {\em vb}, set out.
\item[\gr{>'ekkeimai}]: {\em vb}, be set out, be taken; see \gr{ke~imai}.
\item[\gr{>ekt'ijhmi}]: {\em vb}, set out; see \gr{t'ijhmi}.
\item[\gr{>ekt'oc}]: {\em pre + gen}, outside, external.
\item[\gr{>el'asswn/>el'attwn -on}]: {\em adj}, less, lesser.
\item[\gr{>el'aqistoc -h -on}]: {\em adj}, least.
\item[\gr{>elle'ipw}]: {\em vb}, be less than, fall short of.
\item[\gr{>emp'iptw}]: {\em vb}, meet (of lines), fall on; see \gr{p'iptw}.
\item[\gr{>'emprosjen}]: {\em adv}, in front.
\item[\gr{>enall'ax}]: {\em adv}, alternate(ly).
\item[\gr{>enarm'ozw}]: {\em vb}, insert; {\em perf indic pass 3rd sg}, \gr{>en'hrmostai}.
\item[\gr{>end'eqomai}]: {\em vb}, admit, allow.
\item[\gr{<'eneken}]: {\em ind}, on account of, for the sake of.
\item[\gr{>ennapl'asioc -a -on}]: {\em adj}, nine-fold, nine-times.
\item[\gr{>'ennoia, <h}]: {\em no}, notion.
\item[\gr{enperi'eqw}]: {\em vb}, encompass; see \gr{>'eqw}.
\item[\gr{>enp'iptw}]: see \gr{>emp'iptw}.
\item[\gr{>ent'oc}]: {\em pre + gen}, inside, interior, within, internal.
\item[\gr{<ex'agwnoc -on}]: {\em adj}, hexagonal; \gr{t`o <ex'agwnon},
{\em no}, hexagon.
\item[\gr{<exapl'asioc -a -on}]: {\em adj}, sixfold.
\item[\gr{<ex~hc}]: {\em adv}, in order, successively, consecutively.
\item[\gr{>'exwjen}]: {\em adv}, outside, extrinsic.
\item[\gr{>ep'anw}]: {\em adv}, above.
\item[\gr{>epaf'h, <h}]: {\em no}, point of contact.
\item[\gr{>epe'i}]: {\em conj}, since (causal).
\item[\gr{>epeid'hper}]: {\em ind}, inasmuch as, seeing that.
\item[\gr{>epize'ugn~umi, >epize'uxw,  >ep'ezeuxa}, ---, \gr{>ep'ezeugmai,
>ep'eze'uqjhn}] : {\em vb}, join (by a line).
\item[\gr{>epilog'izomai}]: {\em vb}, conclude.
\item[\gr{>epino'ew}]: {\em vb}, think of, contrive.
\item[\gr{>epip'edoc -on}]: {\em adj}, level, flat, plane; \gr{ t`o >epip'edon}, {\em no}, plane.
\item[\gr{>episk'eptomai}]: {\em vb}, investigate.
\item[\gr{>ep'iskeyic -ewc, <h}]: {\em no}, inspection, investigation.
\item[\gr{>epit'assw}]: {\em vb}, put upon, enjoin; \gr{t`o >epitaqj'en}, {\em no}, the (thing) prescribed; see \gr{t'assw}.
\item[\gr{>ep'itritoc -on}]: {\em adj}, one and a third times. 
\item[\gr{>epif'aneia, <h}]: {\em no}, surface.
\item[\gr{>'epomai}]: {\em vb}, follow.
\item[\gr{>'erqomai,  >ele'usomai, >~hljon, >el'hluja}, ---,  ---]: {\em vb}, come, go.
\item[\gr{>'esqatoc -h -on}]: {\em  adj}, outermost, uttermost, last.
\item[\gr{>eter'omhkhc -ec}]: {\em adj}, oblong; \gr{t`o >eter'omhkec}, {\em no}, rectangle.
\item[\gr{<'eteroc -a -on}]: {\em adj},  other (of two).
\item[\gr{>'eti}]: {\em par}, yet, still, besides.
\item[\gr{e>uj'ugrammoc -on}]: {\em adj}, rectilinear; \gr{t`o e>uj'ugrammon}, {\em no}, rectilinear figure.
\item[\gr{e>uj'uc -e~ia -'u}]: {\em adj}, straight; \gr{<h e>uje~ia}, {\em no}, straight-line; \gr{>ep> e>uje~iac}, in
a straight-line, straight-on.
\item[\gr{e<ur'iskw, e<ur'hskw, h<~uron, e<'ureka, e<'urhmai,  e<ur'ejhn}]:
{\em vb}, find.
\item[\gr{>ef'aptw}]: {\em vb}, bind to; {\em mid}, touch; \gr{<h <efaptom'enh}, {\em no}, tangent; see \gr{<'aptw}.
\item[\gr{>efarm'ozw, >efarm'osw, >ef'hrmosa, >ef'hmoka, >ef'hmosmai, >ef'hm'osjhn}] : {\em vb}, coincide;  {\em pass},  be applied.
\item[\gr{>efex~hc}]: {\em adv}, in order, adjacent.
\item[\gr{>ef'isthmi}]: {\em vb}, set, stand, place upon; see \gr{>'isthmi}.
\item[\gr{>'eqw, <'exw, >'esqon, >'esqhka, -'esqhmai}, ---]: {\em vb}, have.
\item[\gr{<hg'eomai, <hg'hsomai, <hghs'amhn, <hghmai}, ---, \gr{<hg'hjhn}]: {\em vb}, lead.
\item[\gr{>'hdh}]: {\em ind}, already, now.
\item[\gr{<'hkw, <'hxw}, ---,  ---, ---, ---]: {\em vb}, have come, be present.
\item[\gr{<hmik'uklion, t'o}]: {\em no}, semi-circle.
\item[\gr{<hmi'olioc -a -on}]: {\em adj}, containing one and a half, one and
a half times.
\item[\gr{<'hmisuc -eia -u}]: {\em adj}, half.
\item[\gr{>'hper} = \gr{>'h} + \gr{per}]: {\em conj}, than, than indeed.
\item[\gr{>'htoi} \ldots\gr{>'h}]: {\em par},   surely, either \ldots or; 
in fact, either \ldots or.
\item[\gr{j'esic -ewc, <h}]: {\em no}, placing, setting, position.
\item[\gr{jewrhma -atoc, t'o}]: {\em no}, theorem.
\item[\gr{>'idioc -a -on}]: {\em adj}, one's own.
\item[\gr{>is'akic}]: {\em adv}, the same number of times; \gr{>is'akic
pollapl'asia}, the same multiples, equal multiples.
\item[\gr{>isog'wnioc -on}]: {\em adj}, equiangular.
\item[\gr{>is'opleuroc -on}]: {\em adj}, equilateral.
\item[\gr{>isoplhj'hc -'ec}]: {\em adj}, equal in number.
\item[\gr{>'isoc -h -on}]: {\em adj}, equal; \gr{>ex >'isou}, equally, evenly.
\item[\gr{>isoskel'hc -'ec}]: {\em adj}, isosceles.
\item[\gr{>'isthmi, st'hsw, >'esthsa}, ---, ---, \gr{>est'ajhn}]: {\em vb tr}, 
stand (something).
\item[\gr{>'isthmi, st'hsw, >'esthn, <'esthka, <'estamai, >estajhn}]: {\em vb intr}, 
stand up (oneself); Note: perfect {\em I have stood up} can be taken to mean present {\em I am standing}.
\item[\gr{>iso"uy'hc -'ec}]: {\em adj}, of equal height.
\item[\gr{kaj'aper}]: {\em ind}, according as, just as.
\item[\gr{k'ajetoc -on}]: {\em adj}, perpendicular.
\item[\gr{kaj'olou}]: {\em adv}, on the whole, in general.
\item[\gr{kal'ew}]: {\em vb}, call.
\item[\gr{k>akeinoc} = \gr{ka`i >eke~inoc}].
\item[\gr{k>'an} = \gr{ka`i >'an}]: {\em ind}, even if, and if.
\item[\gr{katagraf'h, <h}]: {\em no}, diagram, figure.
\item[\gr{katagr'afw}]: {\em vb}, describe/draw, inscribe (a figure); see \gr{gr'afw}.
\item[\gr{katakolouj'ew}]: {\em vb}, follow after.
\item[\gr{katale'ipw}] : {\em vb}, leave behind; see \gr{le'ipw}; \gr{t`a kataleip'omena}, {\em no},
remainder. 
\item[\gr{kat'allhloc -on}]: {\em adj}, in succession, in corresponding order.
\item[\gr{katametr'ew}]: {\em vb}, measure (exactly).
\item[\gr{katant'aw}]: {\em vb}, come to, arrive at.
\item[\gr{kataskeu'azw}]: {\em vb}, furnish, construct.
\item[\gr{ke~imai, ke~isomai}, ---, ---, ---, ---]: {\em vb}, have been placed,
lie, be made; see \gr{t'ijhmi}.
\item[\gr{k'entron, t'o}]: {\em no}, center.
\item[\gr{kl'aw}]: {\em vb}, break off, inflect.
\item[\gr{kl'inw, kl'inw, >'eklina, k'eklika, k'eklimai, >ekl'ijhn}]: {\em vb}, lean, incline.
\item[\gr{kl'isic -ewc, <h}]: {\em no}, inclination, bending.
\item[\gr{ko~iloc -h -on}]: {\em adj}, hollow, concave.
\item[\gr{koruf'h, <h}]: {\em no}, top, summit, apex; \gr{kat`a koruf'hn},
vertically opposite (of angles).
\item[\gr{kr'inw, krin~w, >'ekr~ina, k'ekrika, k'ekrimai, >ekr'ijhn}]:
{\em vb}, judge.
\item[\gr{k'uboc, <o}]: {\em no}, cube.
\item[\gr{k'ukloc, <o}]: {\em no}, circle.
\item[\gr{k'ulindroc, <o}]: {\em no}, cylinder.
\item[\gr{kurt'oc -'h -'on}]: {\em adj}, convex.
\item[\gr{k~wnoc, <o}]: {\em no}, cone.
\item[\gr{lamb'anw, l'hyomai, >'elabon, e>'ilhfa e>'ilhmmai, >el'hfjhn}]:
{\em vb},\\ take. 
\item[\gr{l'egw}]: {\em vb}, say; {\em pres pass part},
\gr{leg'omenoc -h -on}, {\em adj}, so-called; see \gr{>'eirw}.
\item[\gr{le'ipw, le'iyw, >'elipon, l'eloipa, l'eleimmai, >ele'ifjhn}]: {\em vb}, leave, leave behind.
\item[\gr{lhmm'ation, t'o}]: {\em no}, diminutive of \gr{l~hmma}.
\item[\gr{l~hmma -atoc, t'o}]: {\em no}, lemma.
\item[\gr{l~hyic -ewc, <h}]: {\em no}, taking, catching.
\item[\gr{l'ogoc, <o}]: {\em no}, ratio, proportion, argument.
\item[\gr{loip'oc -'h -'on}]: {\em adj}, remaining.
\item[\gr{manj'anw, maj'hsomai, >'emajon, mem'ajhka}, ---, ---]:  {\em vb}, learn.
\item[\gr{m'egejoc -eoc, t'o}]: {\em no}, magnitude, size.
\item[\gr{me'izwn -on}]: {\em adj}, greater.
\item[\gr{m'enw, men~w, >'emeina, mem'enhka}, ---, ---]: {\em vb}, stay,
remain.
\item[\gr{m'eroc -ouc, t'o}]: {\em no}, part, direction, side.
\item[\gr{m'esoc -h -on}]: {\em adj}, middle, mean, medial; \gr{>ek d'uo m'eswn}, bimedial.
\item[\gr{metalamb'anw}]: {\em vb}, take up.
\item[\gr{metax'u}]: {\em adv}, between.
\item[\gr{met'ewroc -on}]: {\em adj}, raised off the ground.
\item[\gr{metr'ew}]: {\em vb}, measure.
\item[\gr{m'etron, t'o}]: {\em no}, measure.
\item[\gr{mhde'ic, mhdem'ia, mhd'en}]: {\em adj}, not even one, (neut.) nothing.
\item[\gr{mhd'epote}]: {\em adv}, never.
\item[\gr{mhd'eteroc -a -on}]: {\em pro}, neither (of two).
\item[\gr{m~hkoc -eoc, t'o}]: {\em no}, length.
\item[\gr{m'hn}]: {\em par}, truely, indeed.
\item[\gr{mon'ac -'adoc, <h}]: {\em no}, unit, unity.
\item[\gr{monaq'oc -'h -'on}]: {\em adj}, unique.
\item[\gr{monaq~wc}]: {\em adv}, uniquely.
\item[\gr{m'onoc -h -on}]: {\em adj}, alone.
\item[\gr{no'ew}, ---, \gr{n'ohsa, nen'ohka, nen'ohmai, >eno'hjhn}]: {\em vb}, apprehend, conceive.
\item[\gr{o<~ioc -a -on}]: {\em pre}, such as, of what sort.
\item[\gr{>okt'aedroc -on}]: {\em adj}, eight-sided.
\item[\gr{<'oloc -h -on}]: {\em adj}, whole.
\item[\gr{<omogen'hc -'ec}]: {\em adj}, of the same kind.
\item[\gr{<'omoioc -a -on}]: {\em adj}, similar.
\item[\gr{<omoioplhj'hc -'ec}]: {\em adj}, similar in number.
\item[\gr{<omoiotag'hc -'ec}]: {\em adj}, similarly arranged.
\item[\gr{<omoi'othc -htoc, <h}]: {\em no} similarity.
\item[\gr{<omo'iwc}]: {\em adv}, similarly.
\item[\gr{<om'ologoc -on}]: {\em adj}, corresponding, homologous.
\item[\gr{<omotag'hc -'ec}]: {\em adj}, ranged in the same row or line.
\item[\gr{<om'wnumoc -on}]: {\em adj}, having the same name.
\item[\gr{>'onoma -atoc, t'o}]: {\em no}, name; \gr{>ek d'uo >onom'atwn},
binomial.
\item[\gr{>oxug'wnioc -on}]: {\em adj}, acute-angled; \gr{t`o >oxug'wnion},
{\em no}, acute angle.
\item[\gr{>ox'uc -e~ia -'u}]: {\em adj}, acute.
\item [\gr{<opoioso~un} = \gr{<opo~ioc -a -on} + \gr{o>~un}]: {\em adj}, of whatever kind, any kind whatsoever.
\item[\gr{<op'osoc -h -on}]: {\em pro}, as many, as many as.
\item[\gr{<opososdhpoto~un} = \gr{<op'osoc -h -on} + \gr{d'h} + \gr{pot'e} + \gr{o>~un}]: {\em adj},
of whatever number, any number whatsoever.
\item[\gr{<opososo~un} = \gr{<op'osoc -h -on} + \gr{o>~un}]: {\em adj},
of whatever number, any number whatsoever.
\item[\gr{<op'oteroc -a -on}]: {\em pro}, either (of two), which (of two).
\item[\gr{>orjog'wnion, t'o}]: {\em no}, rectangle, right-angle.
\item[\gr{>orj'oc -'h -'on}]: {\em adj}, straight, right-angled, perpendicular; \gr{pr`oc >orj`ac gwn'iac}, at right-angles.
\item[\gr{>'oroc, <o}]: {\em no}, boundary, definition, term (of a ratio).
\item[\gr{<osadhpoto~un} = \gr{<'osa} + \gr{d'h} + \gr{pot'e} + \gr{o>~un}]: {\em ind}, any number\\ whatsoever.
\item[\gr{<os'akic}]: {\em ind}, as many times as, as often as.
\item[\gr{<osapl'asioc -on}]: {\em pro}, as many times as.
\item[\gr{<'osoc -h -on}]: {\em pro}, as many as.
\item[\gr{<'osper, <'hper, <'oper}]: {\em pro}, the very man who, the very thing which.
\item[\gr{<'ostic, <'htic, <'o ti}]: {\em pro}, anyone who, anything which.
\item[\gr{<'otan}]:  {\em adv}, when, whenever.
\item[\gr{<otio~un}]: {\em ind}, whatsoever.
\item[\gr{o>ude'ic, o>udem'ia, o>ud'en}]: {\em pro}, not one, nothing. 
\item[\gr{o<ud'eteroc -a -on}]: {\em pro}, not either.
\item[\gr{o<uj'eteroc}]: see \gr{o<ud'eteroc}.
\item[\gr{o>uj'en}]: {\em ind}, nothing.
\item[\gr{o>~un}]: {\em adv}, therefore, in fact.
\item[\gr{o<'utwc}]: {\em adv}, thusly, in this case.
\item[\gr{p'alin}]: {\em adv}, back, again.
\item[\gr{p'antwc}]: {\em adv}, in all ways.
\item[\gr{par`a}]: {\em prep + acc}, parallel to.
\item[\gr{parab'allw}]: {\em vb}, apply (a figure); see \gr{b'allw}.
\item[\gr{parabol'h, <h}]: {\em no}, application.
\item[\gr{par'akeimai}]: {\em vb}, lie beside, apply (a figure); see \gr{ke~imai}.
\item[\gr{parall'assw, parall'axw,}  ---, \gr{par'hllaqa}, ---, ---]: {\em vb}, miss, fall awry.
\item[\gr{parallhlep'ipedoc, -on}]: {\em adj}, with parallel surfaces; \gr{t`o parallhlep'ipedon}, {\em no}, parallelepiped.
\item[\gr{parallhl'ogrammoc -on}]: {\em adj}, bounded by parallel
lines; \gr{t`o parallhl'ogrammon}, {\em no}, parallelogram.
\item[\gr{par'allhloc -on}]: {\em adj}, parallel; \gr{t`o par'allhlon}, {\em no},
parallel, parallel-line.
\item[\gr{parapl'hrwma -atoc, t'o}]: {\em no}, complement (of a parallelogram).
\item[\gr{parat'eluetoc -on}]: {\em adj}, penultimate.
\item[\gr{par'ek}]: {\em prep + gen}, except.
\item[\gr{paremp'iptw}]: {\em vb}, insert; see \gr{p'iptw}.
\item[\gr{p'asqw, pe'isomai, >'epajon, p'eponja}, ---, ---]: {\em vb}, suffer.
\item[\gr{pent'agwnoc -on}]: {\em adj}, pentagonal; \gr{t`o pent'agwnon},
{\em no}, pentagon.
\item[\gr{pentapl'asioc -a -on}]: {\em adj}, five-fold, five-times.
\item[\gr{pentekaidek'agwnon, t'o}]: {\em no}, fifteen-sided figure.
\item[\gr{peperasm'enoc -h -on}]: {\em adj}, finite, limited; see \gr{per}\-\gr{a'inw}.
\item[\gr{pera'inw, peran~w, >ep'erana}, ---, \gr{peper'asmai, >eperan'anjhn}]: {\em vb}, bring to end, finish, complete; {\em pass},  be finite.
\item[\gr{p'erac -atoc, t'o}]: {\em no}, end, extremity.
\item[\gr{perat'ow}, ---, ---, ---, ---, ---]: {\em vb}, bring to an end.
\item[\gr{perigr'afw}]: {\em vb}, circumscribe; see \gr{gr'afw}.
\item[\gr{peri'eqw}]: {\em vb},
encompass, surround, contain, comprise; see \gr{>'eqw}.
\item[\gr{perilamb'anw}]: {\em vb}, enclose; see \gr{lamb'anw}.
\item[\gr{periss'akic}]: {\em adv}, an odd number of times.
\item[\gr{periss'oc -'h -'on}]: {\em adj}, odd.
\item[\gr{perif'ereia, <h}]: {\em no}, circumference.
\item[\gr{perif'erw}]: {\em vb}, carry round; see \gr{f'erw}.
\item[\gr{phlik'othc -htoc, <h}]: {\em no}, magnitude, size.
\item[\gr{p'iptw, peso~umai, >'epeson, p'eptwka}, ---, ---]: {\em vb}, fall.
\item[\gr{pl'atoc -eoc, t'o}]: {\em no}, breadth, width.
\item[\gr{ple'iwn -on}]: {\em adj}, more, several.
\item[\gr{pleur'a, <h}]: {\em no}, side.
\item[\gr{pl~hjoc -eoc, t'o}]: {\em no}, great number, multitude, number.
\item[\gr{pl'hn}]: {\em adv \& prep + gen}, more than.
\item[\gr{poi'oc -'a -'on}]: {\em adj}, of a certain nature, kind, quality, type.
\item[\gr{pollaplasi'azw}]: {\em vb}, multiply.
\item[\gr{pollaplasiasm'oc, <o}]: {\em no}, multiplication.
\item[\gr{pollapl'asion, t'o}]: {\em no}, multiple.
\item[\gr{pol'uedroc -on}]: {\em adj}, polyhedral; \gr{t'o pol'uedron}, {\em no}, polyhedron.
\item[\gr{pol'ugwnoc -on}]: {\em adj}, polygonal; \gr{t'o pol'ugwnon}, {\em no}, polygon.
\item[\gr{pol'upleuroc -on}]: {\em adj}, multilateral.
\item[\gr{p'orisma -atoc, t'o}]: {\em no}, corollary.
\item[\gr{pot'e}]: {\em ind}, at some time.
\item[\gr{pr~isma -atoc, t'o}]: {\em no}, prism.
\item[\gr{proba'inw}]: {\em vb}, step forward, advance.
\item[\gr{prode'iknumi}]: {\em vb}, show
previously; see \gr{de'iknumi}.
\item[\gr{proekt'ijhmi}]: {\em vb}, set forth beforehand; see \gr{t'ijhmi}.
\item[\gr{proer'ew}]: {\em vb}, say beforehand; 
{\em perf pass part}, \gr{proeirhm'enoc -h -on}, {\em adj}, aforementioned;
see \gr{e>'irw}.
\item[\gr{prosanaplhr'ow}]: {\em vb}, fill up, complete.
\item[\gr{prosanagr'afw}]: {\em vb}, complete (tracing of); see \gr{gr'afw}.
\item[\gr{prosarm'ozw}]: {\em vb}, fit to, attach to.
\item[\gr{prosekb'allw}]: {\em vb}, produce (a line); see \gr{>ekb'allw}.
\item[\gr{proseur'iskw}]: {\em vb}, find besides, find; see \gr{e<ur'iskw}.
\item[\gr{proslamb'amw}]: {\em vb}, add.
\item[\gr{pr'okeimai}]: {\em vb}, set before, prescribe; see \gr{ke~imai}.
\item[\gr{pr'oskeimai}]: {\em vb}, be laid on, have been added to; see \gr{ke~imai}.
\item[\gr{prosp'iptw}]: {\em vb}, fall on, fall toward, meet; see \gr{p'iptw}.
\item[\gr{protasic -ewc, <h}]: {\em no}, proposition.
\item[\gr{prost'assw}]: {\em vb}, prescribe, enjoin; \gr{t`o trostaqj'en}, {\em no}, the thing prescribed; see \gr{t'assw}.
\item[\gr{prost'ijhmi}]: {\em vb}, add; see \gr{t'ijhmi}.
\item[\gr{pr'oteroc -a -on}]: {\em adj}, first (comparative), before, former.
\item[\gr{prot'ijhmi}]: {\em vb}, assign; see \gr{t'ijhmi}.
\item[\gr{proqwr'ew}]: {\em vb}, go/come forward, advance.
\item[\gr{pr~wtoc -a -on}]: {\em adj}, first, prime.
\item[\gr{puram'ic -'idoc, <h}]: {\em no}, pyramid.
\item[\gr{<rht'oc -'h -'on}]: {\em adj}, expressible, rational.
\item[\gr{<romboeid'hc -'ec}]: {\em adj}, rhomboidal; \gr{t`o <romboeid'ec},
{\em no}, romboid.
\item[\gr{<r'omboc, <o}] {\em no}, rhombus.
\item[\gr{shme~ion, t'o}]: {\em no}, point.
\item[\gr{skalhn'oc -'h -'on}]: {\em adj}, scalene.
\item[\gr{stere'oc -'a -'on}]: {\em adj}, solid; \gr{t`o stere'on}, {\em no}, solid, solid body.
\item[\gr{stoiqe~ion, t'o}]: {\em no}, element.
\item[\gr{str'efw, -str'eyw, >'estreya,} ---, \gr{>estammai, >est'afhn}]:
{\em vb}, turn.
\item[\gr{s'ugkeimai}]: {\em vb}, lie together, be the sum of, be composed;\\ \gr{sugke'imenoc -h -on}, {\em adj}, composed (ratio), compounded; see \gr{ke~imai}.
\item[\gr{s'ugkr'inw}]: {\em vb}, compare; see \gr{kr'inw}.
\item[\gr{sumba'inw}]: {\em vb}, come to pass, happen, follow; see
\gr{ba'inw}.
\item[\gr{sumb'allw}]: {\em vb}, throw together, meet; see \gr{b'allw}.
\item[\gr{s'ummetroc -on}]: {\em adj}, commensurable.
\item[\gr{s'umpac -antoc, <o}]: {\em no}, sum, whole.
\item[\gr{sump'iptw}]: {\em vb}, meet together (of lines); see \gr{p'iptw}.
\item[\gr{sumplhr'ow}]: {\em vb}, complete (a figure), fill in.
\item[\gr{sun'agw}]: {\em vb}, conclude, infer; see \gr{>'agw}.
\item[\gr{sunamf'oteroi -ai -a}]: {\em adj}, both together;
\gr{<o sunamf'oteroc}, {\em no}, sum (of two things).
\item[\gr{sunapode'iknumi}]: {\em no}, demonstrate together; see \gr{de'iknumi}.
\item[\gr{sunaf'h, <h}]: {\em no}, point of junction.
\item[\gr{s'unduo, o<i, a<i, t'a}]: {\em no}, two together, in pairs.
\item[\gr{suneq'hc -'ec}]: {\em adj}, continuous; \gr{kat`a t`o suneq'ec}, 
continuously.
\item[\gr{s'unjesic -ewc, <h}]: {\em no}, putting together, composition.
\item[\gr{s'unjetoc -on}]: {\em adj}, composite.
\item[\gr{su[n]'isthmi}]: {\em vb}, construct (a figure), set up together;  {\em perf imperat pass 3rd sg}, \gr{sunest'atw}; see \gr{>'isthmi}.
\item[\gr{sunt'ijhmi}]: {\em vb}, put together, add together, compound (ratio); see \gr{t'ijhmi}.
\item[\gr{sq'esic -ewc, <h}]: {\em no}, state, condition.
\item[\gr{sq~hma -atoc, t'o}]: {\em no}, figure.
\item[\gr{sfa~ira -ac, <h}]: {\em no}, sphere.
\item[\gr{t'axic -ewc, <h}]: {\em no}, arrangement, order.
\item[\gr{tar'assw, tar'axw,} ---, ---, \gr{tet'aragmai, >etar'aqjhn}]: {\em vb}, stir, trouble, disturbe; \gr{tetaragm'enoc -h -on}, {\em adj}, disturbed, perturbed.
\item[\gr{t'assw, t'axw, >'etaxa, t'etaqa, t'etagmai, >et'aqjhn}]: {\em vb},
arrange, draw up.
\item[\gr{t'eleioc -a -on}]: {\em adj}, perfect.
\item[\gr{t'emnw, temn~w, >'etemon, -t'etmhka, t'etmhmai, >etm'hjhn}]:
{\em vb}, cut; {\em pres/fut indic act 3rd sg}, \gr{t'emei}.
\item[\gr{tetarthmorion, t'o}]: {\em no}, quadrant.
\item[\gr{tetr'agwnoc -on}]: {\em adj}, square; \gr{t`o tetr'agwnon},
{\em no}, square.
\item[\gr{tetr'akic}]: {\em adv}, four times.
\item[\gr{tetrapl'asioc -a -on}]: {\em adj}, quadruple.
\item[\gr{tetr'apleuroc -on}]: {\em adj}, quadrilateral.
\item[\gr{tetrapl'ooc -h -on}]: {\em adj}, fourfold.
\item[\gr{t'ijhmi, j'hsw, >'ejhka, t'ejhka, ke~imai, >et'ejhn}]: {\em vb}, place, put.
\item[\gr{tm~hma -atoc, t'o}]: {\em no}, part cut off, piece, segment.
\item[\gr{to'inun}]: {\em par}, accordingly.
\item[\gr{toio~utoc -a'uth -o~uto}]: {\em pro}, such as this.
\item[\gr{tome'uc  -'ewc, <o}]: {\em no}, sector (of circle).
\item[\gr{tom'h, <h}]: {\em no}, cutting, stump, piece.
\item[\gr{t'opoc, <o}]: {\em no}, place, space.
\item[\gr{tosaut'akic}]: {\em adv}, so many times.
\item[\gr{tosautapl'asioc -a -on}]: {\em pro}, so many times.
\item[\gr{toso~utoc  -a'uth -o~uto}]: {\em pro}, so many.
\item[\gr{tout'esti} = \gr{to~ut> >'esti}] : {\em par}, that is to say.
\item[\gr{trap'ezion, t'o}]: {\em no}, trapezium.
\item[\gr{tr'igwnoc -on}]: {\em adj}, triangular; \gr{t`o tr'igwnon}, {\em no},
triangle.
\item[\gr{tripl'asioc -a -on}]: {\em adj}, triple, threefold.
\item[\gr{tr'ipleuroc -on}]: {\em adj}, trilateral.
\item[\gr{tripl-'ooc -h -on}]: {\em adj}, triple.
\item[\gr{tr'opoc, <o}]: {\em no}, way.
\item[\gr{tugq'anw,}] \gr{te'uxomai, >'etuqon, tet'uqhka, t'eteugmai, >ete'u}\-\gr{qjhn} :
{\em vb}, hit, happen to be at (a place).
\item[\gr{<up'arqw}]: {\em vb}, begin, be, exist; see \gr{>'arqw}.
\item[\gr{<upexa'iresic -ewc, <h}]: {\em no}, removal.
\item[\gr{<uperb'allw}]: {\em vb}, overshoot, exceed; see \gr{b'allw}.
\item[\gr{<uperoq'h, <h}]: {\em no}, excess, difference.
\item[\gr{<uper'eqw}]: {\em vb}, exceed; see \gr{>'eqw}.
\item[\gr{<up'ojesic -ewc, <h}]: {\em no}, hypothesis.
\item[\gr{<up'okeimai}]: {\em vb},  underlie, be assumed (as hypothesis); see \gr{ke~imai}.
\item[\gr{<upole'ipw}]: {\em vb}, leave remaining.
\item[\gr{<upote'inw, <upoten~w, <up'eteina, <upot'etaka, <upot'etamai,
<upet'ajhn}]: {\em vb}, subtend.
\item[\gr{<'uyoc -eoc, t'o}]: {\em no}, height.
\item[\gr{faner'oc -'a -'on}]: {\em adj}, visible, manifest.
\item[\gr{fhm`i, f'hsw, >'efhn}, ---, ---, ---]: {\em vb}, say; \gr{>'efamen}, we said.
\item[\gr{f'erw, o>'isw, >'hnegkon, >en'hnoqa, >en'hnegmai, >hn'eqjhn}]:
{\em vb}, carry.
\item[\gr{q'wrion, t'o}]: {\em no}, place, spot, area, figure.
\item[\gr{qwr'ic}]: {\em pre + gen}, apart from.
\item[\gr{ya'uw}]: {\em vb}, touch.
\item[\gr{<wc}]: {\em par}, as, like, for instance.
\item[\gr{<wc <'etuqen}]: {\em par}, at random.
\item[\gr{<wsa'utwc}]: {\em adv}, in the same manner, just so.
\item[\gr{<'wste}]: {\em conj}, so that (causal), hence.
\end{description}}

\onecolumn
\newpage\thispagestyle{empty}~\\
 
